---
title: "Advanced Informatics Week 5 lab"
output: html_document
---

```{r setup, include=FALSE}
library(reticulate)
library(ggplot2)
library(ggpubr)
use_python("/Users/liz/miniconda3/envs/new_env/bin/python",required = T)
knitr::opts_chunk$set(echo = TRUE)
mpl = reticulate::import("matplotlib")
sns = reticulate::import("seaborn")
```

### Plotting basics in base R

```{r}
plot(sin)
```

Change `x` axis label to $\sigma$ and `y` axis label to $\tau$:
```{r}
plot(sin, xlab = expression(sigma), ylab = expression(tau))
```

Change `x` axis label to $\sigma_{s}^2$:
```{r}
plot(sin, xlab=expression(sigma[s]^2))
```

Change line to be red, "dot-dash" style, and 3 times the default thickness:
```{r}
plot(sin, col = "red", lty = 4, lwd = 3)
```

Add title using variable:
```{r}
y = 7
plot(sin, main = bquote(Gamma == .(y)))
```

Add annotation using variable:
```{r}
y = 7
plot(sin)
text(0.1, 0.4, bquote(Gamma == .(y)))
```

Practice saving files:
```{r}
pdf(file="ee283_week5.pdf",
    width = 10, 
    height = 10)
y = 7
par(ps = 18, cex = 1)
plot(sin)
text(0.1, 0.4, bquote(Gamma == .(y)))
dev.off()
```

```{r}
tiff(file="ee283_week5.tiff",
    width = 10, 
    height = 10, units = "in", res = 500)
y = 7
par(ps = 18, cex = 1)
plot(sin,axes=F)
axis(2)
axis(1, cex.axis = 0.5)
text(0.1, 0.4, bquote(Gamma == .(y)))
dev.off()
```

```{r}
png(file="ee283_week5_72res.png",
    width = 10, 
    height = 10, units = "in", res = 72)
y = 7
par(ps = 18, cex = 1)
plot(sin)
text(0.1, 0.4, bquote(Gamma == .(y)))
dev.off()
```

```{r}
png(file="ee283_week5_300res.png",
    width = 10, 
    height = 10, units = "in", res = 300)
y = 7
par(ps = 18, cex = 1)
plot(sin)
text(0.1, 0.4, bquote(Gamma == .(y)))
dev.off()
```

### Plotting basics using ggplot in R
```{r}
library(ggplot2)
data(mtcars)
p = ggplot(mtcars, aes(x=cyl, y = mpg)) + geom_point()
p
```

Change `x` axis label to $\sigma$ and `y` axis label to $\tau$:
```{r}
p1 = p + xlab(expression(sigma)) + ylab(expression(tau))
p1
```

Change `x` axis label to $\sigma_{s}^2$:
```{r}
p2 = p + xlab(expression(sigma[s]^2))
p2
```

Change dots to be red, diamond style, and 3 times the default size:
```{r}
p3 = p + geom_point(color='red', size=3, shape= 18)
p3
```

Add title using variable:
```{r}
y = 7
p4 = p + ggtitle(bquote(Gamma == .(y)))
p4
```

Add annotation using variable:
```{r}
y = 7
p + annotate("text",label = bquote(Gamma == .(y)), x = 4.5, y = 15)
```

Use `ggarrange` to display plots side-by-side:
```{r}
ggarrange(p1, p2, ncol = 2)
```

...and as a 2x2 matrix:
```{r}
ggarrange(p1, p2, p3, p4, nrow = 2, ncol = 2)
```

### Plotting basics using Python

```{python}
import matplotlib.pyplot as plt

f, ax = plt.subplots()
x = [i for i in range(10)]
y = [i**2 for i in x]
ax.plot(x, y);
ax.set_xlabel('x');
ax.set_ylabel('y')
```

Change `x` axis label to $\sigma$ and `y` axis label to $\tau$:
```{python}
f, ax = plt.subplots()
ax.plot(x, y);
ax.set_xlabel('$\\sigma$');
ax.set_ylabel('$\\tau$')
```

Change `x` axis label to $\sigma_{s}^2$:
```{python}
f, ax = plt.subplots()
ax.plot(x, y);
ax.set_xlabel('$\\sigma{_s}{^2}$');
ax.set_ylabel('y')
```

Change line to be red, "dot-dash" style, and 3 times the default size:
```{python}
f, ax = plt.subplots()
ax.plot(x, y, color='red', linestyle='-.',linewidth=3);
ax.set_xlabel('x');
ax.set_ylabel('y')
```

Add title using variable:
```{python}
gamma = 7;
f, ax = plt.subplots()
ax.plot(x, y);
plt.title('$\\Gamma$ = ' + str(gamma));
ax.set_xlabel('x');
ax.set_ylabel('y')
```

Add annotation using variable:
```{python}
gamma = 7;
f, ax = plt.subplots()
ax.plot(x, y);
plt.annotate("$\\Gamma$ = " + str(gamma),xy=(2,30));
ax.set_xlabel('x');
ax.set_ylabel('y')
```

Use `subplots` to display plots side-by-side:
```{python}
f, (ax1, ax2) = plt.subplots(1, 2)
ax1.plot(x, y, color='red', linestyle='-.');
ax2.plot(x, y);
ax1.set_xlabel('x');
ax1.set_ylabel('y');
ax2.set_xlabel('x');
ax2.set_ylabel('y')
```

Use `GridSpec` to display plots as a 2x2 matrix:
```{python}
import matplotlib.gridspec as gridspec
fig2 = plt.figure(constrained_layout=True)
spec2 = gridspec.GridSpec(ncols=2, nrows=2, figure=fig2)
f2_ax1 = fig2.add_subplot(spec2[0, 0])
f2_ax2 = fig2.add_subplot(spec2[0, 1])
f2_ax3 = fig2.add_subplot(spec2[1, 0])
f2_ax4 = fig2.add_subplot(spec2[1, 1])

f2_ax1.plot(x, y);
f2_ax1.set_xlabel('$\\sigma$');
f2_ax1.set_ylabel('$\\tau$');

f2_ax2.plot(x, y);
f2_ax2.set_xlabel('$\\sigma{_s}{^2}$');
f2_ax2.set_ylabel('y');

f2_ax3.plot(x, y, color='red', linestyle='-.');
f2_ax3.set_xlabel('x');
f2_ax3.set_ylabel('y');

f2_ax4.plot(x, y);
plt.title('$\\Gamma$ = ' + str(gamma));
f2_ax4.set_xlabel('x');
f2_ax4.set_ylabel('y');

plt.show()
```
